The 2018 heatwave and its implications on ozone induced damage on vegetation in a subarctic climate

### 2020-04-28 VegOzone.tex
Comments by Ane.

In our assessment of ozone damage on vegetation in the subarctic in relation to the 2018 heatwave, we focus on the NIBIO operated Environment Centre Svanhovd which lies close by the settlement of Svanvik in the Pasvik valley (Section~\ref{subsec:svanhovd}). Throughout the paper, we will use Svanvik synonymously for the atmospheric monitoring site at Svanhovd. The available meteorological monitoring data are described in Section~\ref{subsubsec:atmo_svanvik}. In Section~\ref{subsubsec:ozone_garden}, the ozone garden -- a plant-based ozone monitoring -- will be described in more detail. Other data used for evaluation of the ozone data taken at Svanhovd is described in Section~\ref{subsec:other_data}. We compare with observational data from other monitoring sites in northern Fennoscandia (Section~\ref{subsubsec:ebas}) and use as well reanalysis products (Section~\ref{subsubsec:ozone_rea}) as complement when observational data was not available.

@@

The locations of the atmospheric monitoring site as well as the ozone garden with respect to the main buildings of the Svanhovd Environment Centre are marked in the aerial photography shown in Fig.~\ref{fig:svanhovd_research_station}. The Centre is located south of the settlement of Svanvik, where as the border to Russia, the Pasvik river, lies only a few hundred meters to the east. The original farm buildings, protected by law, are located in the lower center, while the Svanhovd Environment Centre follows to the north-east. The Centre hosts offices, a conference center, a national park center, and a modern laboratory for DNA analysis. Left of the Centre and north of the original farm buildings a botanical garden can be found. It is one amongst three such gardens north of the Polar Circle. The Svanhovd Environment Centre focuses on research of the special environment of the region, but also comprises long-term observations of various agrometeorological variables, i.a. $2\,\unit{m}$ temperature, precipitation, global irradiance, and soil temperature at different depths.

>>>>

In our assessment of ozone damage on vegetation in the subarctic in relation to the 2018 heatwave, we focus on the NIBIO operated Environment Centre Svanhovd which lies close by the settlement of Svanvik in the Pasvik valley (Section~\ref{subsec:svanhovd}). Throughout the paper, we will use Svanhovd synonymously for the atmospheric monitoring site at Svanvik. The available meteorological monitoring data are described in Section~\ref{subsubsec:atmo_svanvik}. In Section~\ref{subsubsec:ozone_garden}, the ozone garden -- a plant-based ozone monitoring -- will be described in more detail. Other data used for evaluation of the ozone data taken at Svanhovd is described in Section~\ref{subsec:other_data}. We compare with observational data from other monitoring sites in northern Fennoscandia (Section~\ref{subsubsec:ebas}) and use as well reanalysis products (Section~\ref{subsubsec:ozone_rea}) as complement when observational data was not available.

@@

The locations of the atmospheric monitoring site as well as the ozone garden with respect to the main buildings of the Svanhovd Environment Centre are marked in the aerial photography shown in Fig.~\ref{fig:svanhovd_research_station}. The Centre is located south of the settlement of Svanvik, where as the border to Russia, the Pasvik river, lies only a few hundred meters to the east. The original farm buildings, protected by law, are located in the lower center, while the Svanhovd Environment Centre follows to the north-east. Left of the Centre and north of the original farm buildings a botanical garden can be found. It is one amongst three such gardens north of the Polar Circle. The Svanhovd Environment Centre focuses on research of the special environment of the region, but also comprises long-term observations of various agrometeorological variables, i.a. $2\,\unit{m}$ temperature, precipitation, global irradiance, and soil temperature at different depths.
